---
title: "Send emails to distribution list"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Bring in email distribution list
```{r}
library(pins)
board_register("rsconnect",
         key = Sys.getenv("CONNECT_API_KEY"),
         server = Sys.getenv("CONNECT_SERVER")
         )

dist_list <- pin_get("katie/distribution", board = "rsconnect")
```

# Compose the email
```{r}
library(blastula)
message <- compose_email(
  body = 
    paste("Good morning, sunshine!", praise::praise())
)
```

# Send the email  

My email provider is gmail-based, so I followed the instructions from https://rich-iannone.github.io/blastula/articles/sending_using_smtp.html
Since I am publishing to Connect and don't want my email credentials being shared, I will pass those as an environment variable using the `pass_envvar` argument in `smtp_send`. See https://github.com/rich-iannone/blastula/issues/149 and PR https://github.com/rich-iannone/blastula/pull/159

```{r}
# Sending email to a personal account
# through manual specification of SMTP
# credentials
message %>%
  smtp_send(
    from = "katie.masiello@rstudio.com",
    to = dist_list$Email, #This will put everyone in the to line
    subject = "Good Morning",
    credentials = creds_envvar(
  user = Sys.getenv("SMTP_USER"),
  pass_envvar = "SMTP_PASSWORD",
  provider = "gmail"
)
  )
```


# Log it
Very simplistic log of email date and who got it:
```{r}
list(Sys.time(), dist_list$Email)
```

